Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-15 sections/acknowledgements.tex

Our research team practices open-source science. All data and analysis code can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab/total_solar_eclipse}. The repository for this paper can be found at \url{https://github.com/UCA-Open-Astronomy-Lab/jurpa_eclipse_paper}

This research would not have been possible without the support of state and federal research grants. Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, matched by ASGC state match 20-ARMF-02. Funding to support student research and travel to present our results came from the ASGC Student Intensive Training award. These ASGC awards are subawards of NASA award number 80NSSC20M0106.

>>>>

Our research team practices open-source science. All data and analysis code, along with the source of this paper can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab}

This research would not have been possible without the support of state and federal grants. Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, matched by ASGC state match 20-ARMF-02. Funding to support student research and travel to present our results came from the ASGC Student Intensive Training award. These ASGC awards are subawards of NASA award 80NSSC20M0106.

### 2025-03-15 sections/conclusion.tex

Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium} and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, falling between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
In future work, we hope to examine the radio lightcurve in detail, with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of th sun, as done in \cite{messerotti_radio_2000}.

>>>>

Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium} and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, falling between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
In future work, we hope to examine the radio lightcurve in detail with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of the sun, as done in \cite{messerotti_radio_2000}.
